### 2012-12-05 doc/description.tex
property: mandatory changed to cardinality

\begin{verbatim}
Class = <label, property*, primitiveCollection*, association*>
Property = <label, App-Type, defaultValue, mandatory>
PrimitiveCollection = <label, App-Type, defaultValue, mandatory>
Association = <label, referencedClass, startCardinality, 
              endCardinality>
App-Type = APP-STRING 
mandatory = Bool
referencesClass = label
startCardinality = NzNat
endCardinality = NzNat
Bool = true | false
NzNat = [0 - 9]*
\end{verbatim}

>>>>

\begin{verbatim}
Class = <label, property*, primitiveCollection*, association*>
Property = <label, App-Type, defaultValue, cardinality>
PrimitiveCollection = <label, App-Type, defaultValue, mandatory>
Association = <label, referencedClass, startCardinality, 
              endCardinality>
App-Type = APP-STRING 
cardinality = NzNat
referencesClass = label
startCardinality = NzNat
endCardinality = NzNat
Bool = true | false
NzNat = [0 - 9]*
\end{verbatim}
